---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(here)
library(usethis)
```

# My-First-Repository

This is my first repository.

It contains several folders with assets.

. Folder 'images' contains jpeg, bmp, and so on files that I need for my documents.
. Folder 'plots' contains images that I generate through code, possibly for publisher.

The function 'print' will display the argument on the screen.
```{r}
print("Hello, World!")
```

# what is your main research interest

My primary research interest lies in **bioinformatics**, specifically the integration of **machine learning** techniques in analyzing large-scale **genomic and microbiome data**. I am fascinated by how computational tools can help unravel complex biological processes, leading to the discovery of novel therapeutic targets. The interdisciplinary nature of this field allows me to merge my passion for biology and programming, and I aim to contribute towards advancing personalized medicine.

# Favorites

## Favorite Music
 1. Perfect , Ed Sheeran 
 2. We can't be friends, Ariana Grande
 3. Illusion, Dua Lipa
 4. Blank Space, Taylor Swift
 5. Someone Like You, Adele

```{r}
 ("C:/Users/sarag/OneDrive/Documents/GEOG.712/My-First-Project/My-First-Repository/Music")
```
## Favorite Equation

$$ E = mc^2 $$
##  Favorite Artists

| Name           | Achievements                          |
|----------------|---------------------------------------|
| Leonardo da Vinci       | Master of both art and science, famous for Mona Lisa and The Last Supper, and his contributions to anatomy and engineering.                         |
| Vincent van Gogh      | Post-impressionist known for Starry Night and Sunflowers, with a bold, emotional style that influenced modern art.                         |
| Pablo Picasso       | Co-founder of Cubism, renowned for Guernica and his innovations in abstraction and form, shaping 20th-century modernism                         |
| Frida Kahlo       | Iconic for her personal self-portraits and her impact on feminist and indigenous representation, as seen in The Two Fridas                         |
| Michelangelo       | Renaissance master known for the David sculpture and the Sistine Chapel ceiling, revolutionizing both art and architecture                        |

# Images 
```{r}
("C:/Users/sarag/OneDrive/Documents/GEOG.712/My-First-Project/My-First-Repository/Images/OIP.jpeg")
```
- My_First_Repository/
    - README.Rmd
    - Music/
        - Favorite musics
    - Images/
        - OIP.jpeg

```{r}
summary(cars)
```
